Fractional Types

### 2016-12-19 typespp.tex
(1/#α)ₖ rule is derivable from dual and inverse
fig:dual
About cong

{\jdg{}{}{(\iorder{\alpha})_k :
 [\iorder{c_1},1/c_1^k]  \leftrightblackspoon
 [\iorder{c_2},1/c_2^k]}}

@@

@@

      \draw (2,0) -- (3,0) -- (3,2) -- (2,2) -- cycle;
      \node at (2.5,1) {\footnotesize{$\texttt{cong}$}};

@@

      \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
      \node at (0.5,1) {\footnotesize{\texttt{cong}}};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

>>>>

@@

\begin{lemma}
  \label{lem:cong}
  For $\mathbb{v} : \mathbb{T}_1 \circledast \mathbb{T}_2$,
  $p : \mathbb{T}_1 \leftrightblackspoon \mathbb{T}$, we have
  $\texttt{cong}^{l}_{p}(\mathbb{v}) : \mathbb{T} \circledast \mathbb{T}_2$, and
  for $q : \mathbb{T}_2 \leftrightblackspoon \mathbb{T}$, we have
  $\texttt{cong}^{r}_{q}(\mathbb{v}) : \mathbb{T}_1 \circledast \mathbb{T}$.
  \begin{proof}
    It follows from the fact that $\circledast$ is an endo-bi-functor.
  \end{proof}
\end{lemma}

@@

      \draw (2,0) -- (3,0) -- (3,2) -- (2,2) -- cycle;
      \node at (2.5,1) {\footnotesize{$\texttt{cong}^{r}$}};

@@

      \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
      \node at (0.5,1) {\footnotesize{$\texttt{cong}^{r}$}};

@@

\begin{figure}
    \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
      \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (0,1);

      \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
      \node at (0.5,1) {\footnotesize{$\unitetl/$}};

      \path (1,1.75) edge node[above] {\footnotesize{$\#id$}} (2,1.75);
      \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#c}}$}} (4,0.25);

      \draw (2,0.75) -- (3,0.75) -- (3,2.75) -- (2,2.75) -- cycle;
      \node at (2.5,1.75) {\footnotesize{$\eta +$}};

      \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#d}$}} (6,2.25);
      \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#d}$}} (4,1.25);

      \draw (4,-0.25) -- (5,-0.25) -- (5,1.75) -- (4,1.75) -- cycle;
      \node at (4.5,0.75) {\footnotesize{\texttt{cong}}};
      \path (4.5,-0.25) edge node[right] {\footnotesize{$p : 1/\#c \leftrightblackspoon 1/\#d$}} (4.5,-0.75);

      \path (5,0.25) edge node[above] {\footnotesize{$1/\textsf{\#d}$}} (6,0.25);
      \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

      \draw (6,0) -- (7,0) -- (7,2.75) -- (6,2.75) -- cycle;
      \node at (6.5,1.375) {\footnotesize{$\synchr$}};

      \path (7,2.25) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (8,2.25);

      \path (7,0.25) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (10,0.25);
      \path (7,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (8,1.25);

      \draw (8,0.75) -- (9,0.75) -- (9,2.75) -- (8,2.75) -- cycle;
      \node at (8.5,1.75) {\footnotesize{$\epsilon +$}};

      \path (9,1.75) edge node[above] {\footnotesize{$\#id$}} (10,1.75);

      \draw (10,0) -- (11,0) -- (11,2) -- (10,2) -- cycle;
      \node at (10.5,1) {\footnotesize{$\unititl/$}};

      \path (11,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (12,1);
    \end{tikzpicture}
    \caption{\label{fig:dual} Dual}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
